Self-tunable approximated explicit MPC: Heat exchanger implementation and analysis

### 2023-07-19 paper/JoPC/cover_letter.tex
cover letter

\documentclass[a4paper,10pt]{letter}
\usepackage{amsmath}
\usepackage{xcolor}
\linespread{1.2}
\begin{document}
\pagestyle{headings}
\begin{letter}{Professor Christos N. Markides, BA (Hons), MEng, MA, PhD, Editor-in-Chief, Applied Thermal Engineering}

\opening{Dear Professor Christos N. Markides,}

@@

We believe that the presented study is, due to its character, of both industrial and academic interest and within the scope of the journal. We would very much appreciate if you would consider the manuscript for publication in the journal Applied Thermal Engineering.

>>>>

\documentclass[a4paper,10pt]{letter}
\usepackage{amsmath}
\usepackage{xcolor}
\linespread{1.2}
\begin{document}
\pagestyle{headings}
\begin{letter}{Professor Martin Guay, Editor-in-Chief, Journal of Process Control}

\opening{Dear Professor Martin Guay,}

@@

We believe that the presented study is, due to its character, of both industrial and academic interest and within the scope of the journal. We would very much appreciate if you would consider the manuscript for publication in the Journal of Process Control.
